pdp: An R Package for Constructing Partial Dependence Plots

### 2016-09-22 manuscript/greenwell.tex
final draft

\title{pdp: An R Package for Creating Partial Dependence Plots}
\author{by Brandon M. Greenwell}

@@

PDPs can be used to graphically examine the dependence of the response on low cardinality subsets of the features, accounting for the average effect of the other predictors. In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{pdp} package. We also briefly discussed related approaches available in other R packages. Suggestions to avoid extrapolation and high exececution times were discussed and demonstrated via examples.

>>>>

\title{pdp: An R Package for Constructing Partial Dependence Plots}
\author{by Brandon M. Greenwell}

@@

PDPs can be used to graphically examine the dependence of the response on low cardinality subsets of the features, accounting for the average effect of the other predictors. In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{pdp} package. We also briefly discussed related approaches available in other R packages. Suggestions to avoid extrapolation and high execution times were discussed and demonstrated via examples.
